\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Shubham Kumar Prajapati} \\ \vspace{1pt}
    \small +91 7080364716 $|$ \href{mailto:jackwill021@gmail.com}{\underline{jackwill021@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/shubham7080/}{\underline{linkedin.com/in/shubham7080}} $|$
    \href{https://github.com/playkashyap}{\underline{github.com/playkashyap}}
\end{center}





%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

      \resumeSubheading
      {Fullstack Developer}{July. 2025 -- Present}
      {Mostedge}{Vadodra, India}
      \resumeItemListStart
        \resumeItem{Building Surveillance application for Keeping Eye on C Stores remotely. With face recognition and logging with GPU acceleration}
        \resumeItem{Developed RESTful APIs with Node.js (TypeScript), python with MSSQL and PostgreSQL. }
        \resumeItem{Actively participating in hosting the Backend with GPU cloud instances.}
        \resumeItem{Used CUDA and Other GPU technologies to speedup the model processing speed with Video encoding and decoding.}
    \resumeItemListEnd

    \resumeSubheading
      {Software Developer (Frontend and Backend)}{Jun. 2023 -- May. 2025}
      {Cosmotech AI}{Noida, India}
      \resumeItemListStart
        \resumeItem{Built responsive UIs using React, Angular, Next.js, HTML, CSS, and TypeScript.}
        \resumeItem{ Developed RESTful APIs with Node.js (TypeScript) and MongoDB for real-time data operations. }
        \resumeItem{Integrated APIs to enhance interactivity and dynamic content.}
        \resumeItem{Used Git for version control; participated in agile ceremonies including sprint planning and daily standups.}
    \resumeItemListEnd

    \resumeSubheading
      {Frontend Developer Intern}{Jan. 2023 -- Jun. 2023}
      {Cosmotech AI}{Noida, India}
      \resumeItemListStart
        \resumeItem{ Contributed to UI development using React, Angular, HTML, CSS, and TypeScript.}
        \resumeItem{Assisted in API integration and dynamic content updates.}
        \resumeItem{Participated in agile processes and collaborated using Git for version control.}
        \resumeItem{Participated in daily stand-ups and team meetings, actively engaging in sprint planning with project goals and timelines.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

% -----company projects -------


\section{Projects with Company}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{HRIS - Front-end} $|$ \emph{Next.js, React, Tailwind, Zustand, Context API, Typescript}}{Aug. 2024 -- May. 2025}
    \resumeItemListStart
      \resumeItem{Developed a pixel-perfect, responsive UI with a custom sidebar using Tailwind and reusable React components.}
      \resumeItem{Built a dynamic drag-and-drop dashboard for customizable user workflows and widget arrangements.}
      \resumeItem{Managed global state efficiently using Zustand and Context API across multiple modules.}
      \resumeItem{Created custom dynamic organizational chart which can be exported to a pdf.}
    \resumeItemListEnd

     \resumeProjectHeading
    {\textbf{PMS - Front-end} $|$ \emph{Angular, RxJs, Bootstrap, Apex Charts, Ngrx, Typescript}}{July. 2023 -- May. 2025}
         \resumeProjectHeading
    {\textbf{Rate System - Front-end} $|$ \emph{React, Vite, Bootstrap, Apex Charts, Context API, Javascript}}{Jan. 2023 -- May. 2025}
    
\resumeSubHeadingListEnd



%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{HandFlow} $|$ \emph{Python, OpenCV, Mediapipe, CNN, TensorFlow, NumPy }}{Aug. 2022 -- Apr. 2023}
          \resumeItemListStart
          \resumeItem{A proposed Framework for Controlling Basic Computer Functionalities with Hand Gesture}
          \resumeItem{Created a real-time video program with 96\% accuracy for static gestures and 97\% accuracy for dynamic gestures, employing a robust process encompassing data collection, model training, and real-time implementation.}
          \resumeItem{Executed diverse computer functions based on recognized gestures, including actions like zooming, saving, and minimizing open windows.}

          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Image Processing based Brain Tumor Detection} $|$ \emph{Python, SVM}}{Aug. 2021 -- Jan. 2022}
          \resumeItemListStart
            \resumeItem {Applied advanced algorithms, including pre-processing, segmentation, and SVM classification, to enhance accuracy in brain tumor detection}
            \resumeItem{Published a paper titled "Image Processing based Brain Tumor Detection" at ICFIRTP-2022.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, HTML/CSS, Typescript, MongoDB, GraphQL, SQL(beginer)} \\
     \textbf{Frameworks}{: ReactJs, Node.js, Express.js, Tailwind,  Bootstrap, Material-UI, Angular, NextJs} \\
     \textbf{Developer Tools}{: Git, Git Version control, VS Code, MongoDB Atlas, Postman, MongoDB Compass, MS Azure} \\
     \textbf{Libraries}{: MUI, Rxjs, Axios, Body Parser, bCrypt, JWT, Moment, Angular Material, ThreeJs, ShadCn UI, Tenstack}
    }}
 \end{itemize}

 %-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Sharda University}{Gr Noida, India}
      {Bachelor of Computer Science and Technology}{Aug. 2019 -- Aug. 2023}
  \resumeSubHeadingListEnd
    \resumeSubHeadingListStart
    \resumeSubheading
      {Columbus International School}{Ballia, India}
      {Higher Secondry, {81\%}}{Mar. 2016 -- Apr. 2018}
  \resumeSubHeadingListEnd
    \resumeSubHeadingListStart
    \resumeSubheading
      {Columbus International School}{Ballia, India}
      {Secondry ,{10 CGPA}}{Mar. 2014 -- Mar. 2016}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
